On hyperparameter tuning through Lipschitz global optimization

### 2023-08-22 2023/ITMO paper/elsarticle-template-num.tex
add author information
fix table

@@

>>>>

\begin{table}[]
\caption{14 datasets used in the experiments.}
\label{tab:1}
\begin{tabular}{lllllll}
\hline
Name                                                            & Num   & Attributes & Int & Float & Categorical & Classes \\ \hline
Balance                                                         & 625   & 4          & 4   & 0     & 0           & 3       \\
Bank Marketing                                                  & 45211 & 20         & 6   & 4     & 10          & 2       \\
Banknote                                                        & 1372  & 4          & 0   & 4     & 0           & 2       \\
Breast Cancer                                                   & 569   & 9          & 9   & 0     & 0           & 2       \\
CarEvaluation                                                   & 1728  & 6          & 0   & 0     & 6           & 4       \\
CNAE9                                                           & 1080  & 856        & 856 & 0     & 0           & 9       \\
Credit Approval                                                 & 690   & 15         & 0   & 6     & 9           & 2       \\
Digits                                                          & 5620  & 64         & 64  & 0     & 0           & 10      \\
Ecoli                                                           & 336   & 7          & 0   & 7     & 0           & 8       \\
Parkinsons                                                      & 197   & 22         & 0   & 22    & 0           & 2       \\
Semeion                                                         & 1593  & 256        & 256 & 0     & 0           & 10      \\
\begin{tabular}[c]{@{}l@{}}Statlog \\ Segmentation\end{tabular} & 2310  & 19         & 1   & 18    & 0           & 7       \\
Wilt                                                            & 4889  & 5          & 0   & 5     & 0           & 2       \\
Zoo                                                             & 101   & 16         & 16  & 0     & 0           & 7       \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[]
\caption{Время поиска значений гиперпараметров при однократном запуске алгоритма оптимизации.}
\label{tab:3}
\begin{tabular}{lllllll}
\hline
Dataset &
  \begin{tabular}[c]{@{}l@{}}Optuna \\ random\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Optuna \\ tpe\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Optuna \\ cmaes\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Optuna \\ nsgaii\end{tabular} &
  \begin{tabular}[c]{@{}l@{}}Hyperopt\\ tpe\end{tabular} &
  iOpt \\ \hline
Balance                                                         & 10.8   & 9.2    & 9.0    & 10.6   & 10.3   & 7.7    \\
\begin{tabular}[c]{@{}l@{}}Bank \\ Marketing\end{tabular}       & 2888.5 & 3406.5 & 2704.7 & 3078.6 & 3190.3 & 2963.3 \\
Banknote                                                        & 31.9   & 12.0   & 17.7   & 22.1   & 21.7   & 18.4   \\
\begin{tabular}[c]{@{}l@{}}Breast \\ Cancer\end{tabular}        & 9.3    & 7.6    & 6.3    & 8.1    & 8.5    & 6.0    \\
CarEvaluation                                                   & 50.9   & 63.3   & 51.0   & 53.1   & 69.5   & 45.2   \\
CNAE9                                                           & 295.6  & 207.6  & 318.4  & 262.2  & 253.5  & 144.9  \\
\begin{tabular}[c]{@{}l@{}}Credit \\ Approval\end{tabular}      & 14.2   & 12.6   & 13.4   & 13.4   & 15.8   & 10.8   \\
Digits                                                          & 132.8  & 57.5   & 82.1   & 111.6  & 92.4   & 62.5   \\
Ecoli                                                           & 5.5    & 6.3    & 4.0    & 5.4    & 6.4    & 3.6    \\
Parkinsons                                                      & 3.5    & 5.0    & 3.6    & 3.8    & 4.4    & 2.9    \\
Semeion                                                         & 218.4  & 119.5  & 157.9  & 135.7  & 193.6  & 114.2  \\
\begin{tabular}[c]{@{}l@{}}Statlog \\ Segmentation\end{tabular} & 156.1  & 55.4   & 87.1   & 159.2  & 91.6   & 66.5   \\
Wilt                                                            & 70.0   & 75.8   & 68.5   & 67.4   & 78.2   & 60.9   \\
Zoo                                                             & 3.0    & 3.9    & 3.0    & 3.1    & 4.2    & 1.8    \\ \hline
\end{tabular}
\end{table}
